master thesis

### 2017-08-08 Masterarbeit - Latex/Masterarbeit - Lydia Buntrock - v1.tex
update structure
Former-commit-id: f2e49ed78ba080615cc1aca228a49230eb30c079

  A. Introduction. The thesis must clearly state its theme, hypotheses and/or goals (sometimes 
    called “the research question(s)”), and provide sufficient background information to enable a 
    non-specialist scholar to understand them. It must contain a thorough review of relevant 
    literature, perhaps in a separate chapter. \\

  B. Research/Scholarship Chapters. The account of the scholarly work should be presented in a 
    manner suitable for the field. It should be complete, systematic, and sufficiently detailed to 
    enable a reader to understand how the data were gathered and analyzed, and how to apply similar 
    methods in another study. Notation and formatting must be consistent throughout the thesis, 
    including units of measure, abbreviations, and the numbering scheme for tables, figures, 
    footnotes, and citations. One or more chapters may consist of material published (or submitted
    for publication) elsewhere, or other artifacts (e.g., film, application-oriented documents) 
    placed in a scholarly context. See “Including Published Material in a Thesis or Dissertation” 
    for additional details. \\

  C. Conclusion. In this section the student must demonstrate his/her mastery of the field and 
    describe the work's overall contribution to the broader discipline in context. A strong 
    conclusion includes the following:
    \begin{itemize}
      \item Conclusions regarding the goals or hypotheses presented in the Introduction,
      \item Reflective analysis of the scholarly work and its conclusions in light of current 
        knowledge in the field,
      \item Comments on the significance and contribution of the scholarship reported,
      \item Comments on strengths and limitations of the research/scholarship,
      \item Discussion of any potential applications of the findings, and
      \item A description of possible future research directions, drawing on the work reported.
    \end{itemize}
    A submission's success in addressing the expectations above is appropriately judged by experts 
      in the relevant discipline. Students should rely on their research supervisors and committee 
      members for guidance. Doctoral students should also take into account the expectations 
      articulated in the University's “Instructions for Preparing the External Examiner's Report”.

%---------------------------------------------------------------------------------------------------
%---------------------------------------------------------------------------------------------------
%--------------------------------------------------------------------------------------------------- 
\chapter{Introduction}
  On the first page, you should present
  \begin{itemize}
    \item The area of research (e.g. implementation of information systems)
    \item The most relevant previous findings in this area
    \item Your research problem and why this is worthwhile studying
    \item The objective of the thesis: how far you hope to advance knowledge in the field
  \end{itemize}
  Target group \\
  To whom are you writing, what do you assume that the reader know? A normal target groupd would be 
    new Master students. \\
  Personal motivation \\
  Why did you choose this topic? \\
  Research method in brief \\
  How will you find out? \\
  Structure of the report \\
  A paragraph about each chapter. What is the main contribution of the chapter? How do they relate? \\

@@

%---------------------------------------------------------------------------------------------------
%---------------------------------------------------------------------------------------------------
%--------------------------------------------------------------------------------------------------- 
\chapter{CRelated literature and theoretical focus}
  A survey of the literature (journals, conferences, book chapters) on the areas that are relevant 
    to your research question. One section per area. \\
  The chapter should conclude with a summary of the previous research results that you want to 
    develop further or challenge. The summary could be presented in a model, a list of issues, etc. 
    Each issue could be a chapter in the presentation of results. They should definitely be 
    discussed in the discussion / conclusion of the thesis.

%---------------------------------------------------------------------------------------------------
%---------------------------------------------------------------------------------------------------
%--------------------------------------------------------------------------------------------------- 
\chapter{Presentation of the part of the world to be studied}
  Which could be the health system in Mozambique, the rural areas where the telecentres are located, 
    the financial businesses in which the accounting system you will develop will be used.

%---------------------------------------------------------------------------------------------------
%---------------------------------------------------------------------------------------------------
%--------------------------------------------------------------------------------------------------- 
\chapter{Method}
  The research method by which you will investigate the world.
  \begin{itemize} 
    \item A short summary of the available methods
    \item Your choice
    \item Detailed report of how you actually carried out your research. Presenting how you selected 
      the people taking part is of special importance.
  \end{itemize}

%---------------------------------------------------------------------------------------------------
%---------------------------------------------------------------------------------------------------
%--------------------------------------------------------------------------------------------------- 
\chapter{... Your research results (and discussion)}
  Which could be the system you made and the reasons for various design decisions, what your 
    interview objects said, observations of people using a computer system, stories of a development 
    process, numeral data from a questionnaire, etc. \\
  The discussion of the findings can be included in these chapters, or the discussion can be put in 
    a separate chapter.  \\
  The issues from the theory chapter (chapter 2) should be discussed here.

%---------------------------------------------------------------------------------------------------
%---------------------------------------------------------------------------------------------------
%--------------------------------------------------------------------------------------------------- 
\chapter{Conclusion}
  Summary of the problem, the main findings and the discussion. Structured according to the issues 
    in chapter 2. \\
  Comparison with the literature presented in chapter 2: how do your results fill in, advance or 
    contradict previously reported research? \\
  What are the implications of your research for people working in the field that you have studies? \\
  In which direction should further research go?  \\

>>>>

%---------------------------------------------------------------------------------------------------
%---------------------------------------------------------------------------------------------------
%--------------------------------------------------------------------------------------------------- 
\chapter{Introduction}
  A. Introduction. The thesis must clearly state its theme, hypotheses and/or goals (sometimes 
    called “the research question(s)”), and provide sufficient background information to enable a 
    non-specialist scholar to understand them. It must contain a thorough review of relevant 
    literature, perhaps in a separate chapter. \\

  On the first page, you should present
  \begin{itemize}
    \item The area of research (e.g. implementation of information systems)
    \item The most relevant previous findings in this area
    \item Your research problem and why this is worthwhile studying
    \item The objective of the thesis: how far you hope to advance knowledge in the field
  \end{itemize}
  Target group \\
  To whom are you writing, what do you assume that the reader know? A normal target groupd would be 
    new Master students. \\
  Personal motivation \\
  Why did you choose this topic? \\
  Research method in brief \\
  How will you find out? \\
  Structure of the report \\
  A paragraph about each chapter. What is the main contribution of the chapter? How do they relate? \\

@@

%---------------------------------------------------------------------------------------------------
%---------------------------------------------------------------------------------------------------
%--------------------------------------------------------------------------------------------------- 
\chapter{Research/Scholarship}
  The account of the scholarly work should be presented in a 
    manner suitable for the field. It should be complete, systematic, and sufficiently detailed to 
    enable a reader to understand how the data were gathered and analyzed, and how to apply similar 
    methods in another study. Notation and formatting must be consistent throughout the thesis, 
    including units of measure, abbreviations, and the numbering scheme for tables, figures, 
    footnotes, and citations. One or more chapters may consist of material published (or submitted
    for publication) elsewhere, or other artifacts (e.g., film, application-oriented documents) 
    placed in a scholarly context. See “Including Published Material in a Thesis or Dissertation” 
    for additional details. \\

  %---------------------------------------------------------------------------------------------------
  %--------------------------------------------------------------------------------------------------- 
  \section{Related literature and theoretical focus}
    A survey of the literature (journals, conferences, book chapters) on the areas that are relevant 
      to your research question. One section per area. \\
    The chapter should conclude with a summary of the previous research results that you want to 
      develop further or challenge. The summary could be presented in a model, a list of issues, etc. 
      Each issue could be a chapter in the presentation of results. They should definitely be 
      discussed in the discussion / conclusion of the thesis.

  %---------------------------------------------------------------------------------------------------
  %--------------------------------------------------------------------------------------------------- 
  \section{Presentation of the part of the world to be studied}
    Which could be the health system in Mozambique, the rural areas where the telecentres are located, 
      the financial businesses in which the accounting system you will develop will be used.

  %---------------------------------------------------------------------------------------------------
  %--------------------------------------------------------------------------------------------------- 
  \section{Method}
    The research method by which you will investigate the world.
    \begin{itemize} 
      \item A short summary of the available methods
      \item Your choice
      \item Detailed report of how you actually carried out your research. Presenting how you selected 
        the people taking part is of special importance.
    \end{itemize}

  %---------------------------------------------------------------------------------------------------
  %--------------------------------------------------------------------------------------------------- 
  \section{... Your research results (and discussion)}
    Which could be the system you made and the reasons for various design decisions, what your 
      interview objects said, observations of people using a computer system, stories of a development 
      process, numeral data from a questionnaire, etc. \\
    The discussion of the findings can be included in these chapters, or the discussion can be put in 
      a separate chapter.  \\
    The issues from the theory chapter (chapter 2) should be discussed here.

%---------------------------------------------------------------------------------------------------
%---------------------------------------------------------------------------------------------------
%--------------------------------------------------------------------------------------------------- 
\chapter{Conclusion}
  C. Conclusion. In this section the student must demonstrate his/her mastery of the field and 
    describe the work's overall contribution to the broader discipline in context. A strong 
    conclusion includes the following:
    \begin{itemize}
      \item Conclusions regarding the goals or hypotheses presented in the Introduction,
      \item Reflective analysis of the scholarly work and its conclusions in light of current 
        knowledge in the field,
      \item Comments on the significance and contribution of the scholarship reported,
      \item Comments on strengths and limitations of the research/scholarship,
      \item Discussion of any potential applications of the findings, and
      \item A description of possible future research directions, drawing on the work reported.
    \end{itemize}
    A submission's success in addressing the expectations above is appropriately judged by experts 
      in the relevant discipline. Students should rely on their research supervisors and committee 
      members for guidance. Doctoral students should also take into account the expectations 
      articulated in the University's “Instructions for Preparing the External Examiner's Report”.

  Summary of the problem, the main findings and the discussion. Structured according to the issues 
    in chapter 2. \\
  Comparison with the literature presented in chapter 2: how do your results fill in, advance or 
    contradict previously reported research? \\
  What are the implications of your research for people working in the field that you have studies? \\
  In which direction should further research go?  \\
